---
title: 'Seminar: Introduction to statistical analysis of areal data'
subtitle: "Application Presentation"
author: "Sven Maurice Morlock"
date: "`r Sys.Date()`"
output:
  beamer_presentation: default
bibliography: ../assets/references.bib
header-includes:
  - \setbeamertemplate{navigation symbols}{}
  - \setbeamertemplate{footline}[page number]
  - \usepackage{relsize}
  - \usepackage{multicol}
  - \usepackage[font=small,labelfont=bf]{caption}
  - \usepackage{nonfloat}
  - \setlength{\columnsep}{+2.5cm}
---
```{r, echo = FALSE, include = FALSE}
source("functions.R")
source("segmentation.R")
#knitr::opts_chunk(include = FALSE)
path_assets_folder <- file.path(path_project_root, "assets")
```
# Motivation I

\begin{multicols}{2}
    \includegraphics[width=95mm]{../assets/spatial-signal-example.pdf}
\columnbreak
  \begin{itemize}
    \item Corona cases in Germany
    \item We can see some regional patterns
    \item Can some districts be clustered?
  \end{itemize}
\end{multicols}

# Motivation II
```{r data-description, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "signal-description-1.pdf"))
```

# Setup I

- data on corona cases in Germany for years 2020 to 2022

- 396 districts (2 non-adjacent)

- interpret each district as vertex/node

- (initial) edge weight 1/0 if districts adjacent or not

- Spatial segmentation/clustering based on @graph_seg_paper via adaptive ridge
  
  - only one 'spatial signal' no other variables are taken into account
  
  - spatial signal ${\mathrel{\widehat{=}}}$ $\frac{\text{cummulative cases in period}}{\text{avg. population in period}}$

# Setup II (adaptive ridge)

- in each iteration $l$:

  - calculate new weights $v_{k}$
  
  - calculate new signal $\theta_{k}$
  
  - minimize $l^{pen}(\boldsymbol{\theta}, \mathcal{V}^{l}) = l(\boldsymbol{\theta}) + \frac{\lambda}{2} + \Sigma_{j\sim k}v_{j,k}^{(l)}(\theta_{j} - \theta_{i})^{2}$
  
- after successful iteration we will end up with new signals for each district 

- but due to regularization some districts will have the same signal (we are penalizing difference in signals)

- districts having same signal assigned to same cluster

- this is done for some schedule of $\lambda$ values 
  - $\rightsquigarrow$ assessment after each iteration cycle by AIC/BIC/GCV


# Results I

```{r results-1, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "penalization-paths.pdf"))
```


# Results II (2020)

```{r results-2, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "segmentation-2020-min.pdf"))
```

# Results III (2021)

```{r results-3, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "segmentation-2021-min.pdf"))
```

# Results IV (2022)

```{r results-4, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "segmentation-2022-min.pdf"))
```


# Discussion

- We can see different results depending on chosen IC and time period

- By design only 1 variable (graph signal) is considered

  - no covariates included
  
  - but also no notion of dependent/independent variable as in regression
  
- limited interpretation

# Backup

# Backup

- Adaptive ridge iteratively optimizes:

\begin{equation} \boldsymbol{\theta}^{(l)} = (\boldsymbol{\Sigma}^{-1} + \lambda \boldsymbol{K}^{(l-1)})^{-1}\boldsymbol{\Sigma}^{-1} \boldsymbol{x} \end{equation}
  
\begin{equation}  v_{j,k}^{(l)} = \frac{1}{(\theta_{j}^{(l)} - \theta_{k}^{(l)})^{2} + c} \end{equation}

# Backup
```{r backup-1, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "result-2022-factornumeric.pdf"))
```

# Backup

```{r backup-2, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "result-2022-regpath.pdf"))
```

# Backup

```{r backup-3, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "constant-signal-wave-1.pdf"))
```

# Backup

```{r backup-4, echo = FALSE}
knitr::include_graphics(file.path(path_assets_folder, "constant-signal-wave-2.pdf"))
```

# References